\documentclass{resume}
\usepackage{tabto}
\usepackage[none]{hyphenat}

\usepackage{amssymb}
\usepackage{url}

\renewcommand{\categoryfont}{\sc}

%
% set the space used for category titles here:
% use the same value for oddsidemargin and marginparwidth [the latter 
% 		will be reset to account for marginparsep]
% 
\setlength{\oddsidemargin}{1.1in}
\setlength{\marginparwidth}{1.1in}
% 
% calculate other dimensions [textwidth and evensidemargin] 
% in function of oddsidemargin and marginparwidth: 
% would be nicer to put in the class file...
%
\addtolength{\marginparwidth}{-\marginparsep}
 \setlength{\evensidemargin}{\oddsidemargin}
 \setlength{\textwidth}{\paperwidth}
 \addtolength{\textwidth}{-2in}
 \addtolength{\textwidth}{-2\oddsidemargin}
 \addtolength{\textwidth}{\marginparwidth}
 \addtolength{\textwidth}{\marginparsep}
%
%
\setlength{\topmargin}{-0.5in}
%
%
\renewcommand{\labelcitem}{$\rhd$}
\renewcommand{\labelitemi}{$\cdot$}
\newcommand{\first}{$1^{\mbox{\scriptsize st}}$\ }
\newcommand{\second}{$2^{\mbox{\scriptsize nd}}$\ }
\newcommand{\third}{$3^{\mbox{\scriptsize rd}}$\ }

\author{~~~~~~Michael J. Wilcox}
% ------ Address -------------------------------------------------------

\address{
	14 Mill Pond Road \tabto{13cm} mwilcox56@gmail.com\\
	Washington, NJ 07882 \tabto{11.73cm} http://mikewilcox.nfshost.com\\
	908 235 66360
	}

\begin{document}
\maketitle

\begin{category}{Objective}
\citemnobullet
To obtain a full-time job as a computer programmer.
\end{category}

% ------- Education ---------------------------------------------------

\begin{category}{Education}
\citem{Rutgers University}, New Brunswick, NJ\\
B.S. in Computer Science, expected graduation December 2012.\\
Major GPA 3.12
\end{category}

\begin{category}{Skills}
\citemnobullet 
C, C++, Java, Python, Ruby, PHP, Javascript, HTML, CSS, SQL, Wordpress, Apache, Git, Vim, Maple, \LaTeX, Scheme, Prolog.
\end{category}

\begin{category}{Operating Systems}
\citemnobullet
Ubuntu, UNIX, Mac OS X, Windows.\\
\end{category}

\begin{category}{Relevant Courses}
\citemnobullet
Artificial Intelligence (current), Computer Architecture, Principles of Database Management, Data Structures, Design and Analysis of Computer Algorithms (current), Discrete Structures I, Discrete Structures II, Internet Technology, Introductory Java Programming, Introduction to Computer Graphics (current), Introduction to Imaging and Multimedia, Multivariable Calculus, Programming Principles, Software Methodology (current), Systems Programming (current).\\
\end{category}

\begin{category}{Work Experience}
\citem{Junior Web Developer}, Fifth Room Creative;
March 2011--July 2012.\\
Custom Wordpress Development. Integrated client development requirements into a friendly user maintainable Wordpress website. Worked both on backend and frontend development using Javascript, PHP, SQL, HTML, and CSS. Implemented Google Maps web app that gave customer real time visual map data of the company distribution centers across the globe using the Google Maps API.%

\citem{Web Developer}, Washington Township;
July 2009--May 2011.\\
Assisted with frequent updates to township website. Worked primarily in NetObjects Fusion. %

\citem{IT Support Technician}, Centocor;
May 2006--September 2006.\\
Worked in company IT help center installing operating systems on employee machines and troubleshooting hardware problems. Assisted with upgrading specific types of printers throughout the company. Helped to organize company inventory room, saving company through refurbishment of old equipment. %

\citem{Intern}, McNeil Consumer;
May 2005--August 2005.\\
Helped with updates to company intranet website in Dreamweaver. Assisted with project to migrate database servers.%
\end{category}

\begin{category}{Projects}
\citem{Stock Recommendation Website}\\
Wrote two web scraping programs in Python that scraped stock recommendations from a forum and stored them into a CSV file. Re-factored Java code to load a large CSV file into a database re-writing all the Java logic in SQL. Created, developed, and launched a website written mainly in PHP which retrieves information stored in a MySQL database in a simple yet quick manner. \\
\mbox{\small\tt https://github.com/mjw56/webScrape}\\
\mbox{\small\tt cs336-41.rutgers.edu}
\end{category}


% -------- Reference --------------------------------------------

\begin{category}{References, Publications} 
\citem{Tomasz Imielinski}\\
imielins@cs.rutgers.edu \\
\citem{Steve Guberman}\\
steveg@fifthroomcreative.com\\
\end{category}

\begin{category}{Interests}
\citemnobullet
Running, Music, Web Development, Arduino.
\end{category}

\end{document}
